Response to reviews of ``Quantifying the effects of single mutations on viral escape from broad and narrow antibodies to an H1 influenza hemagglutinin'' from \textit{Nature Microbiology}

### 2018-01-22 paper/NatureMicrobiologyReviews.tex
shortened reviewer response a bit

{\color{black}
This is true.
Our approach systematically quantifies how all \emph{single} mutations affect viral neutralization.
This contrasts with an alternative approach of using multiple rounds of growth to select for multi-mutants.
There are strengths and weaknesses to both approaches.
Examining all single mutations makes the results complete and quantitative---but we can't make claims about the effects of multiple mutations.
In contrast, multi-cycle growth sometimes finds combinations of mutations, but is not complete and quantitative, since there are too many multiple mutants to examine them all, and it is random which mutations arise in any given multi-cycle growth experiment.
In particular, multi-cycle growth assays do not generate data that can be quantitatively compared across antibodies using the methods here.
Therefore, the strength of our approach (examining all single mutations in a way that is comparable across antibodies) comes with the limitation that we do not find multiple mutants.

We have taken the following pains to emphasize this limitation. 
First, the title of the paper reads ``Quantifying the effects of \emph{single mutations} on viral escape from broad and narrow antibodies to an H1 influenza hemagglutinin'' (emphasis added). 
Stating this fact in the title makes the limitation immediately and directly clear.

@@

{\color{black}
The reviewer is correct that A/WSN/1933 is a lab-adapted virus.
As the reviewer notes, in his/her comment, this is not necessarily a problem for our work since we are simply examining antibody neutralization rather than pathogenesis, fitness, or transmission. 
Nonetheless, the reviewer is correct that it is important to clearly mention this caveat. 
We have now added the following text when we first discuss this strain:

@@

{\color{black}
This is a good comment that was also made by several other reviewers.
We therefore now do as suggested by showing full data for triplicate measurements with significance testing.

Specifically, all the neutralization assays with FI6v3 were performed in triplicate on the same day to eliminate batch effects, with each replicate involving independent serial dilution of the antibody in a separate column of a 96-well plate (this is now more fully explained in the Methods).
In the original manuscript, we only showed the mean and standard deviation in Figure~6A.
We have now added a supplementary figure (Figure~S9) that shows all the replicates.
In addition, as explained in the legend to the new Figure~S9, we fit IC50 values to each replicate, and then use the three IC50's to test the null hypothesis that each mutant has an IC50 indistinguishable from wildtype.

The statistical testing results in Figure~S9B support the conclusions in the text. 
The four mutations that are \emph{not} expected to differ from wildtype with respect to FI6v3 neutralization (K280A, V135T, P80D, and M17L(HA2)) do \emph{not} have IC50s that are significantly different than wildtype.
The four mutations expected to have the largest increases in neutralization resistance (K280S, G47R(HA2), K280T, and N291S) are all significantly more resistant to FI6v3 than wildtype, with corrected $P$-values ranging from 0.00072 to 0.023.
The mutation found by our mutational antigenic profiling but that elicited the most skepticism both from us and the reviewers is K(-8)T.
However, the statistical testing suggests that it really is slightly but significantly more resistant to FI6v3, with a corrected $P$-value of 0.04. 
But we agree that the effect is very small, and in the revised text we clearly emphasize this fact and advise caution in over-interpreting the result:

@@

{\color{black}
The reviewer is correct that we do not include biophysical measurements of why the mutants have increased neutralization resistance.
However, biophysically characterizeing antibody binding to the mutants is beyond the scope of the current study.
We are careful to avoid making any claims about the mechanisms of the mutations---we simply say that they reduce neutralization.
This is in line with many other studies in the field.
While biophysically oriented studies certainly include such measurements, there are numerous papers on viral evolution and antibody breadth that characterize neutralization as the phenotype of interest.
Our study falls into this latter class.
}

@@

{\color{black}
Thank you for pointing out these two important references, which we now discuss.
Two additional references were pointed out by Reviewer \#3.
We also think it is interesting that all of these studies selected their escape mutants in group 2 HAs rather than a group 1 HA like the one in our study.
Anecdotally, it seems to us that there are more described broad anti-stalk antibodies against group 1 than group 2 HAs.
We obviously have no way to quantify this rigorously, but in the added text that mentions the two studies suggested by the reviewer, we also point out the difference in HA groups:

@@

{\color{black}
We see the rationale behind this suggestion, but do we not believe it is essential for the current work. 
Our claim is that we specifically identify mutations that increase resistance to each of the individual monoclonal antibodies.
With the three broad antibodies tested in this paper (FI6v3, C179, S139/1) and the four narrow antibodies tested by Doud et al (2017), we have now examined seven different antibodies.
The only overlap between antibodies in the identified resistance mutations comes when those antibodies target similar epitopes (e.g., FI6v3 and C179)---there is no overlap in the mutations identified by antibodies targeting different epitopes.
This fact indicates that we are identifying bona fide resistance mutations to the specific antibodies used, rather than mutations with some general effect on all IgGs.

Figure~6 provides further data indicating that these are genuine antibody-specific resistance mutations rather than mutations generally selected by any IgG.
For instance, the mutations that increase resistance to H17-L19 (V135T) or H17-L7 (P80D) do not affect neutralization by FI6v3, demonstrating that they are specific to the antibodies that selected them.
Finally, we note that there are numerous published papers where the same monoclonal antibody is tested against a wide range of viral variants for the purposes of comparing IC50s across viruses without also including data showing that all viral variants are unaffected by an irrelevant antibody (e.g., Table~1 of \textit{Nature}, 489:526-532; Figure~3 of \textit{Nature Microbiology},; 2:16199).
}

@@

{\color{black}
All of the results for the broadly neutralizing antibodies are new to this study.
The reviewer is correct that the data for the narrow antibodies in Figure 6B,C is from Doud et al (2017), and the mutational tolerance data in Figure 7 is from Doud and Bloom (2016).
This fact is clearly stated; for instance, the figure legends say ``Shown are neutralization curves for representative escape mutants from H17-L19 and H17-L7 taken from Doud et al (2017)'' and ``The logo plots at bottom show the preference of each HA site of each amino acid under selection for viral replication as measured by Doud and Bloom (2016).''
There is nothing wrong with including previous data for comparative purposes.
For instance, new reports of protein crystal structures often compare the results to prior structures, and often include these prior structures in figures for points of comparison.
In fact, a major strength of our approach is that it puts how mutations affect neutralization into units that can be meaningfully compared across studies.

The experimental methodology is the same as in Doud et al (2017), although the entire analysis framework (all Equations in the paper, not just Equations 10 and 11) are new.
The strength of this analysis framework is that it enables the results to be quantitatively compared across antibodies, which was not possible with the approach in Doud et al (2017). 
}

@@

{\color{black}
We certainly agree that it would be interesting to examine additional strains.
However, prior to our work, no study had ever completely mapped the effect of all single mutations to any viral strain with respect to neutralization by any broadly neutralizing influenza antibody, so we believe that just doing this with one strain is a sufficient step forward in knowledge to be valuable.
As mentioned in the response to question 2 by Reviewer \#1, we now more clearly explain that WSN is a lab-adapted strain.
}

@@

{\color{black}
The neutralization assays in Figure~6 show that the mutations for the stalk-targeting antibodies only have weak effects on neutralization, while Figure~7 shows that many of them don't have much effect on viral growth.
In addition, we were able to generate all of the stalk-antibody mutations for the neutralization assays, so they are not too badly attenuated for viral fitness in cell culture.
However, we avoid making strong statements about the effects of mutations on viral growth beyond the data in Figure~7 because it is beyond the scope of our study to do growth curves for such a large number of mutations.}

@@

{\color{black}
We examined all amino-acid changes, including those that involved multiple-nucleotide changes.
The reason is that our libraries contained all codon mutations (e.g., the 63 non-wildtype codons at each site) rather than just all single nucleotide mutations.
We have added text that clarifies this point:
\begin{quote}
\textsl{Importantly, as described previously (Doud and Bloom 2016), these virus libraries were generated by mutagenizing HA at the \emph{codon} level rather than at the nucleotide level.
Performing codon mutagenesis is important, because single-nucleotide mutations access only about a third of the possible amino-acid mutations from a given codon, whereas codon mutations access all possible amino-acid mutations.}
\end{quote}
}

@@

{\color{black}
We agree that this is an important caveat, and it was also mentioned by other reviewers.
See our response to question 1 by Reviewer \#1 for how we have addressed this caveat.}

@@

{\color{black}
This is a good point, and was also made by several other reviewers.

We have provided a detailed response in answer to question 5 by Reviewer \#1.
Our revisions include showing the neutralization curves for all replicates and performing statistical testing.
All the neutralization curves for antibody FI6v3 were performed on the same day.
This is important because as the reviewer notes, there can be batch effects.
If you look at Figure~6, you will see that the wildtype curves in panels A, B, and C are slightly different since each was performed a different day.
But each panel is for a single antibody, and all curves with that antibody were performed on the same day---we repeated the wildtype in each batch of assays to avoid any confounding batch effects.
Therefore, we have already done what the reviewer suggests, and the new Figure~S9 now clearly explains this.

As described in the response to question 5 by Reviewer \#1, the new statistical analysis finds that the effect for K(-8)T is significant, whereas that for K280A is not.
We agree that the effect for K(-8)T is somewhat perplexing.
In the original manuscript, we said, \textsl{``we are not confident that this effect exceeds the noise in our neutralization assays.''}.
However, the new statistical analysis described in response to question 5 by Reviewer \#1 finds the effect is significant, but we continue to add strong caveats (see the response to question 5 by Reviewer \#1). 
So rest assured that we are not trying to exaggerate the effect of K(-8)T; we sincerely wish it would go away as it would simplify the reviewer responses!
However, this mutation was identified by our mutational antigenic profiling (which was performed in triplicate), and then again by a totally independent approach (neutralization assays, again performed in triplicate). 
So in good conscience, we feel that we have to present the result with K(-8)T, however perplexing.

The reviewer also points out that it might be interesting to look at the $F_{r,a}$ value for K280A, since it might have reduced neutralization resistance.
First, we note that the statistical analysis in the new Figure~S9 shows that the difference between K280A and wildtype is \emph{not} statistically significant, so we do not comment on possible increased neutralization sensitivity or the $F_{r,a}$ for this mutation in the paper.
However, we have added a new supplementary file (File~S6) that gives all the $F_{r,a}$ values in case anyone wants to examine them.
The value of $F_{r,a}$ for this mutation is 0.00382, which is slightly below the library average of 0.00955.
}

@@

{\color{black}
For the quantitative analyses of IC50 values, we fit four-parameter logistic curves, although we fixed the top value to one, so there are really only three parameters.
This is now explained in the legend to the new Figure~S9, which reports the actual IC50 values and shows the curves for individual replicates.
The exact computer code used to fit the curves is at \url{https://jbloomlab.github.io/dms_tools2/dms_tools2.neutcurve.html}.
}

@@

{\color{black}
We are disappointed that the reviewer does not view the work of sufficient impact for \textit{Nature Microbiology}, but are appreciative of the statement that the study is ``performed to an extremely high technical standard.''
We feel that direct quantitative comparison of the escape from narrow and broad antibodies is valuable, since other comparisons have been more anecdotal.
We also note that at least two of the four reviewers found the work to be of high impact.
Therefore, we think it is appropriate for \textit{Nature Communications}.

Thank you for the references mentioned above. 
Interestingly, references 3, 4, and 6 all describe selecting escape from \emph{group 2} HAs (e.g., H3 or H7), not a group 1 HA like the one we have used.
We now cite these references and mention this point as described in the response to question 7 by Reviewer \#1.
It is true that reference 5 mentioned by the reviewer does mention an escape mutation from a group 1 HA from CR6261, but it never actually shows any neutralization data for that mutation, so we are unable to comment on it in detail.
}

@@

{\color{black}
The original paper on C179 selected a strong escape mutant virus in an H1 background.
That virus had three mutations, and although the authors argue in the text that only one of them is important, they never actually show that the others are not required as secondary changes.
We cite this paper, and use it to inform the discussion of multiple mutants that is described in response to question 1 from Reviewer \#1.
}

@@

{
\color{black}
This question was also asked by other reviewers.
We now better describe the neutralization curves, show curves for all replicates, calculate IC50s and the statistical significance of their differences from wildtype, and describe the curve fitting procedures.
These revisions are detailed in response to question 5 of Reviewer \#1 and questions 5 and 6 of Reviewer \#2.}

@@

{\color{black}
We are unable to answer this question, because the concentrations of any given antibody specificity can vary widely among people.
In addition, it is difficult to relate \textit{in vitro} neutralization to \textit{in vivo} activity due to Fc-mediated effector functions.
This is a limitation not just of our study, but of virtually all work on antibody neutralization.
We mention this caveat in the Discussion:
\begin{quote}
\textsl{When interpreting the magnitude of these effects, it is important to note that our experiments only measure how mutations affect neutralization, and not how they affect Fc-mediated functions that are responsible for much of the in vivo protection afforded by anti-stalk antibodies.}
\end{quote}
}

@@

{\color{black}
This is an important question.
Unfortunately, most of the antibodies have been characterized against only a very small number of the very large number of strains within HA subtypes.
We summarize the subtype-level information in Figure 2B, and cite all studies that look at breadth within subtypes (references 24, 25, 29, 45, 46).
However, because different studies use different strains, the data in these studies do not enable useful comparisons across antibodies.
Our study only looks at one strain---but at least it is complete for the mutations to this HA, and so can be compared across antibodies.}

@@

{\color{black}
This is a good reference, and we now cite it at the relevant point.
Interestingly, the distribution of infection frequencies they derive from epidemiology is similar to the 4-7 years we had previously cited from a human challenge study.
However, we have updated the text to say ``$\sim$5 years'' to better reflect the ambiguity.}

>>>>

{\color{black}
This is true.
Our approach systematically quantifies how all \emph{single} mutations affect viral neutralization.
This contrasts with an alternative approach of using multiple rounds of growth to select for multi-mutants.
There are strengths and weaknesses to both approaches.
Examining all single mutations makes the results complete and quantitative---but we can't make claims about the effects of multiple mutations.
In contrast, multi-cycle growth sometimes finds combinations of mutations, but is not complete and quantitative, since it is random which mutations arise in any given multi-cycle growth experiment.
Therefore, the strength of our approach (examining all single mutations in a way that is comparable across antibodies) comes with the limitation that we do not find multiple mutants.

We have taken the following pains to emphasize this limitation. 
First, the title of the paper reads ``Quantifying the effects of \emph{single mutations} on viral escape from broad and narrow antibodies to an H1 influenza hemagglutinin'' (emphasis added).

@@

{\color{black}
The reviewer is correct that A/WSN/1933 is a lab-adapted virus.
As the reviewer also notes, this is not actually a problem for our work since we are examining antibody neutralization rather than pathogenesis, fitness, or transmission. 
Nonetheless, the reviewer is correct that it is important to clearly mention this caveat. 
We have added the following text:

@@

{\color{black}
This is a good comment that was also made by several other reviewers.
We therefore now show full data for triplicate measurements with significance testing.

Specifically, all neutralization assays with FI6v3 were performed in triplicate on the same day to eliminate batch effects, with each replicate involving independent serial dilution of the antibody in a separate column of a 96-well plate (this is now explained in the Methods).
In the original manuscript, we only showed the mean and standard deviation in Figure~6A.
We have added Figure~S9, which shows all the replicates.
In addition, as explained in Figure~S9, we fit IC50 values to each replicate, and used the three IC50's to test the null hypothesis that each mutant has an IC50 indistinguishable from wildtype.

The statistical testing in Figure~S9B supports the conclusions in the text. 
The four mutations that are \emph{not} expected to differ from wildtype with respect to FI6v3 neutralization (K280A, V135T, P80D, and M17L(HA2)) do \emph{not} have IC50s that are significantly different than wildtype.
The four mutations expected to have the largest increases in neutralization resistance (K280S, G47R(HA2), K280T, and N291S) are all significantly more resistant to FI6v3 than wildtype, with corrected $P$-values ranging from 0.00072 to 0.023.
The mutation found by our mutational antigenic profiling that elicited the most skepticism both from us and the reviewers is K(-8)T.
However, the statistical testing suggests that it really is slightly but significantly more resistant to FI6v3, with a corrected $P$-value of 0.04. 
However the effect is very small, and in the revised text we clearly emphasize this fact and advise caution in over-interpreting the result:

@@

{\color{black}
The reviewer is correct that we do not include biophysical measurements of why the mutants have increased neutralization resistance.
However, biophysically characterizeing antibody binding is beyond the scope of our study.
We do not make any claims about the mechanisms of the mutations---we simply say that they reduce neutralization.
This is in line with many other studies in the field.
While biophysically oriented studies certainly include such measurements, there are numerous papers on viral evolution and antibody breadth that characterize neutralization as the phenotype of interest.
Our study falls into this latter class.
}

@@

{\color{black}
Thank you for pointing out these important references, which we now discuss.
Two more references were pointed out by Reviewer \#3.
Interestingly, all these studies selected their escape mutants in group 2 HAs rather than a group 1 HA like the one in our study.
Anecdotally, it seems that there are more described broad anti-stalk antibodies against group 1 than group 2 HAs.
We obviously have no way to quantify this rigorously, but in the added text that mentions the studies suggested by the reviewer, we also point out the difference in HA groups:

@@

{\color{black}
We see the rationale behind this suggestion, but do we not believe it is essential for the current work. 
Our claim is that we specifically identify mutations that increase resistance to each of the individual antibodies.
With the three broad antibodies tested in this paper (FI6v3, C179, S139/1) and the four narrow antibodies tested by Doud et al (2017), we have examined seven different antibodies.
The only overlap in the identified resistance mutations comes when the antibodies target similar epitopes (e.g., FI6v3 and C179)---there is no overlap in the mutations identified by antibodies targeting different epitopes.
This fact indicates that we are identifying bona fide resistance mutations, rather than mutations with some general effect on all IgGs.

Figure~6 provides further data indicating that we find antibody-specific resistance mutations rather than mutations generally selected by any IgG.
For instance, the mutations that increase resistance to H17-L19 (V135T) or H17-L7 (P80D) do \emph{not} affect neutralization by FI6v3, showing they are specific to the antibodies that selected them.
Finally, note that there are numerous papers where a monoclonal antibody is tested against a range of viral variants to compare IC50s without including data showing that all viral variants are unaffected by an irrelevant antibody (e.g., Table~1 of \textit{Nature}, 489:526-532; Figure~3 of \textit{Nature Microbiology},; 2:16199).
}

@@

{\color{black}
All the results for the broadly neutralizing antibodies are new to this study.
The data for the narrow antibodies in Figure 6B,C is from Doud et al (2017), and the mutational tolerance data in Figure 7 is from Doud and Bloom (2016).
This fact is clearly stated; for instance, the figure legends say ``Shown are neutralization curves for representative escape mutants from H17-L19 and H17-L7 \emph{taken from Doud et al (2017)}'' and ``The logo plots at bottom show the preference of each HA site of each amino acid under selection for viral replication \emph{as measured by Doud and Bloom (2016)}.''
There is nothing wrong with including previous data for comparative purposes.
For instance, papers on crystal structures often compare the results to prior structures on related molecules.
In fact, a major strength of our approach is that it puts the results into units that can be meaningfully compared across studies.

The experimental methodology is the same as in Doud et al (2017), although the entire analysis framework (all equations, not just Equations 10 and 11) are new.
The strength of this framework is that it enables the results to be compared across antibodies, which was not possible with the approach in Doud et al (2017). 
}

@@

{\color{black}
We agree that it would be interesting to examine additional strains.
However, prior to our work, no study had completely mapped the effect of all single mutations to any viral strain with respect to neutralization by any broad antibodies---so doing this with one strain is a substantial step forward.
As mentioned in the response to question 2 by Reviewer \#1, we now more clearly explain that WSN is a lab-adapted strain.
}

@@

{\color{black}
The neutralization assays in Figure~6 show that mutations for the stalk-targeting antibodies only have weak effects on neutralization, while Figure~7 shows that many of them don't have much effect on viral growth.
In addition, we were able to generate all the stalk-antibody escape mutants for the neutralization assays, so they are not too badly attenuated in cell culture.
However, we avoid making strong statements about the effects of mutations on viral growth beyond the data in Figure~7 because it is beyond the scope of our study to do growth curves for such a large number of mutations.}

@@

{\color{black}
Our study tested all amino-acid changes, including those that involved multiple-nucleotide changes.
The reason is that our libraries contained all codon mutations (e.g., the 63 non-wildtype codons at each site) rather than just all single nucleotide mutations.
We have added text that clarifies this point:
\begin{quote}
\textsl{Importantly, as described previously (Doud and Bloom 2016), these virus libraries were generated by mutagenizing HA at the \emph{codon} level rather than at the nucleotide level.
Performing codon mutagenesis is important, because single-nucleotide mutations access only about a third of the possible amino-acid mutations from a given codon, whereas codon mutations access all possible amino-acid mutations.}
\end{quote}
}

@@

{\color{black}
We agree that this is an important caveat.
See our response to question 1 by Reviewer \#1.}

@@

{\color{black}
A similar point was made by several other reviewers.
We have provided a detailed response in answer to question 5 by Reviewer \#1.

Our revisions showithe neutralization curves for all replicates and performing statistical testing.
All neutralization curves for antibody FI6v3 were performed on the same day.
This is important because as the reviewer notes, there can be batch effects.
If you look at Figure~6, you will see that the wildtype curves in panels A, B, and C are slightly different.
But each panel is for a single antibody, and all curves with with each antibody were performed on the same day to avoid any confounding batch effects.
Therefore, we have already done what the reviewer suggests, and the new Figure~S9 now clearly explains this.

As described in the response to question 5 by Reviewer \#1, the new statistical analysis finds that the effect for K(-8)T is significant, whereas that for K280A is not.
The reviewer also suggests that it might be interesting to look at the $F_{r,a}$ value for K280A, since it might have reduced neutralization resistance.
Since the statistical analysis in the new Figure~S9 shows that the difference between K280A and wildtype is \emph{not} statistically significant, we do not comment on possible increased neutralization sensitivity or the $F_{r,a}$ for this mutation in the paper.
However, we have added a new supplementary file (File~S6) that gives all the $F_{r,a}$ values.
The value of $F_{r,a}$ for this mutation is 0.00382, which is slightly below the library average of 0.00955.
}

@@

{\color{black}
For the quantitative analyses of IC50's, we fit four-parameter logistic curves, although we fixed the top value to one.
This is explained in the legend to the new Figure~S9, which reports the IC50's and shows the curves for individual replicates.
The computer code used to fit the curves is at \url{https://jbloomlab.github.io/dms_tools2/dms_tools2.neutcurve.html}.
}

@@

{\color{black}
We are disappointed that the reviewer does not view the work of sufficient impact for \textit{Nature Microbiology}, but appreciate the statement that the study is ``performed to an extremely high technical standard.''
We feel that direct quantitative comparison of the escape from narrow and broad antibodies is valuable, since other comparisons have been more anecdotal.
We also note that at least two of the reviewers found the work of high impact.

Thank you for the references. 
Interestingly, (3), (4), and (6) all describe selecting escape from \emph{group 2} HAs (e.g., H3 or H7), not a group 1 HA like the one we used.
We now cite these references and mention this point as described in the response to question 7 by Reviewer \#1.
It is true that (5) does mention an escape mutation from a group 1 HA from CR6261, but it never actually shows any neutralization data for that mutation, so we are unable to comment on it.
}

@@

{\color{black}
The original paper on C179 selected a strong escape mutant in an H1 background.
That virus had three mutations, and although the paper argues that only one is important, it never shows that the others are not required as secondary changes.
We cite this paper, and use it to inform the discussion of multiple mutants described in response to question 1 from Reviewer \#1.
}

@@

{
\color{black}
This point was also mentioned by other reviewers.
See our response to question 5 of Reviewer \#1 and questions 5 and 6 of Reviewer \#2.}

@@

{\color{black}
We are unable to answer this question, because the concentrations of any given antibody specificity can vary widely among people.
In addition, it is difficult to relate \textit{in vitro} neutralization to \textit{in vivo} activity due to Fc-mediated effector functions.
This is a limitation of virtually all work on antibody neutralization.
We mention this caveat in the Discussion:
\begin{quote}
\textsl{When interpreting the magnitude of these effects, it is important to note that our experiments only measure how mutations affect neutralization, and not how they affect Fc-mediated functions that are responsible for much of the in vivo protection afforded by anti-stalk antibodies.}
\end{quote}
}

@@

{\color{black}
Unfortunately, most of the antibodies have been characterized against only a small number of the many strains within HA subtypes.
We summarize the subtype-level information in Figure 2B, and cite all studies that look at breadth within subtypes (references 24, 25, 29, 45, 46).
However, because different studies use different strains, the data in these studies do not enable useful comparisons across antibodies.
Our study only looks at one strain---but at least it is complete for the mutations to this HA, and so can be compared across antibodies.}

@@

{\color{black}
This is a good reference, and we now cite it.
The distribution of infection frequencies they derive from epidemiology is similar to the 4-7 years we had previously cited from a human challenge study.
However, we have updated the text to ``$\sim$5 years'' to better reflect the ambiguity.}
